Measurement and Probability in Fuzzy Quantum Theories

### 2017-04-28 prop_iop.tex
prop_iop.tex Update preamble...
prop_iop.tex \section{Quantum Real-valued and Interval-valued Probability Measures\label{sec:Real-and-Interval}} Updating...

\theoremstyle{plain}
\newtheorem{thm}{Theorem}
\newtheorem{lemma}[thm]{Lemma}
\newtheorem{cor}[thm]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[thm]{Definition}
\newtheorem{example}[thm]{Example}

@@

Similarly, we can recast the result of cryptodeterminism to quantum
interval-valued probability measures as well. In another word, for
any classically event space~$\events$,there is always a classical
interval-valued probability measure~$\bar{\mu}:\events\rightarrow\left\{ \imposs,\necess\right\} $.
However, given a Hilbert space of dimension~$d\ge3$, there is no
quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\left\{ \imposs,\necess\right\} $
by corollary~\ref{cor:Kochen-Specker-IVPM} of the Kochen-Specker
theorem. The Kochen-Specker theorem provides an example that quantum
interval-valued probability measures behave differently from the classical
one, and the convexity and core in the next section provides another
example that quantum interval-valued probability measures behave unexpectedly.

@@

@@

\begin{proof}We are going to prove by contradiction! Suppose there
is a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\left\{ \imposs,\necess\right\} $.
Consider $\mu:\events\rightarrow\left[0,1\right]$ defined by
\begin{equation} 
\mu(P)=\cases{ 
0 & if $\bar{\mu}(P)=\imposs$ ;\\ 
1 & if $\bar{\mu}(P)=\necess$ .
}\end{equation}
We are going to verify that $\mu$ is a cryptodeterministic measure
so that contradicts to the Kochen-Specker theorem.
\begin{itemize}
\item Since $\bar{\mu}(\mathbb{0})=\imposs$, we have $\mu(\mathbb{0})=0$.
\item Since $\bar{\mu}(\mathbb{1})=\necess$, we have $\mu(\mathbb{1})=1$.
\item For every event $P$, we have 
\begin{equation}\eqalign{ 
& \pmeas\left(P\right)=0\\ 
\Rightarrow & \bar{\mu}(P)=\imposs\\
\Rightarrow & \bar{\mu}(\Omega\backslash P)=\left[1,1\right]-\imposs=\necess\\
\Rightarrow & \pmeas\left(\Omega\backslash P\right)=1=1-\pmeas\left(P\right)\textrm{ .}
}\end{equation}
Similarly, when $\pmeas\left(P\right)=1$, we also have $\pmeas\left(\Omega\backslash P\right)=1-\pmeas\left(P\right)$.
\item Given a collection $\left\{ P_{i}\right\} _{i=1}^{N}$ of pairwise
disjoint events. 
\begin{itemize}
\item If $\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=1$, then we have $\necess=\bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})$
so that $\necess=\sum_{i=1}^{N}\bar{\mu}(P_{i})$, i.e., $\sum_{i=1}^{N}\pmeas(P_{i})=1=\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)$.
\item If $\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=0$, then we have $\imposs=\bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})$
so that $\imposs=\sum_{i=1}^{N}\bar{\mu}(P_{i})$, i.e., $\sum_{i=1}^{N}\pmeas(P_{i})=0=\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)$.
\end{itemize}
\end{itemize}
\end{proof}

@@

>>>>

\theoremstyle{plain}
\newtheorem{thm}{Theorem}
\newtheorem{lemma}[thm]{Lemma}
\newtheorem{cor}[thm]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[thm]{Definition}
\newtheorem{example}[thm]{Example}
\theoremstyle{remark}
\newtheorem{claim}[thm]{Claim}

@@

Similarly, we can recast the result of cryptodeterminism to quantum
interval-valued probability measures as well. In another word, for
any classically event space~$\events$,there is always a classical
interval-valued probability measure mapping to $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $.
However, given a Hilbert space of dimension~$d\ge3$, there is no
quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$
by corollary~\ref{cor:Kochen-Specker-IVPM} of the Kochen-Specker
theorem. The Kochen-Specker theorem provides an example that quantum
interval-valued probability measures behave differently from the classical
one, and the convexity and core in the next section provides another
example that quantum interval-valued probability measures behave unexpectedly.

@@

Previously we discussed how to construct a quantum IVPM from a quantum
real-valued probability measure; we then switch our focus to how to
construct a quantum real-valued probability measure from a special
kind of quantum IVPM.

\begin{lemma}\label{lemma:QIVPM2QCM}Let $\mathscr{I}_{\mathrm{D}}$
be $\left\{ \imposs,\necess\right\} $. Given a quantum interval-valued
probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$,
$\mu:\events\rightarrow\left[0,1\right]$ defined by 
\begin{equation} 
\mu(P)=\cases{ 
0 & if $\bar{\mu}(P)=\imposs$ ;\\ 
1 & if $\bar{\mu}(P)=\necess$ ,
}\end{equation}
 is a cryptodeterministic measure.\end{lemma}

\begin{proof}~
\begin{itemize}
\item Since $\bar{\mu}(\mathbb{0})=\imposs$, we have $\mu(\mathbb{0})=0$.
\item Since $\bar{\mu}(\mathbb{1})=\necess$, we have $\mu(\mathbb{1})=1$.
\item For every event $P$, we have 
\begin{equation}\eqalign{ 
& \pmeas\left(P\right)=0\\ 
\Rightarrow & \bar{\mu}(P)=\imposs\\
\Rightarrow & \bar{\mu}(\Omega\backslash P)=\left[1,1\right]-\imposs=\necess\\
\Rightarrow & \pmeas\left(\Omega\backslash P\right)=1=1-\pmeas\left(P\right)\textrm{ .}
}\end{equation}
Similarly, when $\pmeas\left(P\right)=1$, we also have $\pmeas\left(\Omega\backslash P\right)=1-\pmeas\left(P\right)$.
\item Given a collection $\left\{ P_{i}\right\} _{i=1}^{N}$ of pairwise
disjoint events. 
\begin{itemize}
\item If $\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=1$, then we have $\necess=\bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})$
so that $\necess=\sum_{i=1}^{N}\bar{\mu}(P_{i})$, i.e., $\sum_{i=1}^{N}\pmeas(P_{i})=1=\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)$.
\item If $\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=0$, then we have $\imposs=\bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})$
so that $\imposs=\sum_{i=1}^{N}\bar{\mu}(P_{i})$, i.e., $\sum_{i=1}^{N}\pmeas(P_{i})=0=\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)$.
\end{itemize}
\end{itemize}
\end{proof}

Together with the Kochen-Specker theorem, we will have the following
corollary.

@@

@@

Our next lemma discusses the Choquet integral on the real-valued probability
measure reduced to the conventional expectation value.

After we defined the expectation value, we can provide another proof
of corollary~\ref{cor:Kochen-Specker-IVPM} which doesn't refer the
Kochen-Specker theorem directly.

\begin{thm}\label{cor:Kochen-Specker-expectation}Given a Hilbert
space of dimension~$d\ge3$, there is no quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$,
where $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
as before.\end{thm}

\begin{proof}Assume there is a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$,
we will prove $\bar{\mu}$ has such bizarre properties that it cannot
exist.\end{proof}
